17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-03-22 rules/rules22.tex
updated benchmark syntax (mainly for proof track)

Benchmark files are in the concrete syntax of the SMT-LIB format
version~2.6, though with a \emph{restricted} set of commands.  A benchmark
file is a text file containing a sequence of SMT-LIB commands that
satisfies the following \emph{requirements}:
%
\begin{itemize}
  \item \bkey{(set-logic ...)}\\
    A (single) \akey{set-logic} command is the \emph{first} command after
    any \akey{set-option} commands.
  \item \bkey{(set-info ...)}\\
    A benchmark file may contain any number of \akey{set-info} commands.
  \item
    \bkey{(set-option ...)}
    \begin{enumerate}[label=(\alph*)]
      \vspace{-1ex}
    \item The Input may contain the following \akey{set-option} commands.
    \item In the \emph{\inctrack}, the \akey{:print-success} option
      must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
    \item In all other tracks, the scrambler will add an initial
      \akey{(set-option :print-success false)} command to the solver.
    \item In the \emph{\mvaltrack}, a benchmark file contains a single
      \akey{(set-option :produce-models true)} command as the second command.
    \item In the \emph{\ucoretrack}, a benchmark file contains a
      single \akey{(set-option :produce-unsat-cores true)} command as
      the second command.
    \end{enumerate}
  \item \bkey{(declare-sort ...)}\\
    A benchmark file may contain any number of \akey{declare-sort} and
    \akey{define-sort} commands.  All sorts declared or defined with these
    commands must have zero arity.
  \item \bkey{(declare-fun ...)} and \bkey{(define-fun ...)}\\
    A benchmark file may contain any number of \akey{declare-fun} and
    \akey{define-fun} commands.
  \item \bkey{(declare-datatype ...)} and \bkey{(declare-datatypes ...)}\\
    If the logic features algebraic datatypes, the benchmark file may
    contain any number of \akey{declare-datatype(s)} commands.
  \item \bkey{(assert ...)}\\
    A benchmark file may contain any number of \akey{assert} commands.  All
    formulas in the file belong in the declared logic, with any free symbols
    declared in the file.
  \item
    \bkey{:named}
    \begin{enumerate}[label=(\alph*)]
      \vspace{-1ex}
      \item In \emph{all} tracks \emph{except} the \ucoretrack,  named
        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
        used.
      \item In the \emph{\ucoretrack}, top-level assertions may be named.
    \end{enumerate}
    \item
      \bkey{(check-sat)}
      \begin{enumerate}[label=(\alph*)]
        \vspace{-1ex}
        \item In \emph{all} tracks \emph{except} the \inctrack, there is
          \emph{exactly one} \akey{check-sat} command.
        \item In the \emph{\inctrack}, there are one or more
        \akey{check-sat} commands.  There may also be zero or more
        \akey{(push 1)} commands, and zero or more \akey{(pop 1)} commands,
        consistent with the use of those commands in the SMT-LIB standard.
    \end{enumerate}
    \item \bkey{(get-unsat-core)}\\
      In the \emph{\ucoretrack}, the \akey{check-sat} command (which is
      always issued in an unsatisfiable context) is followed by a single
      \akey{get-unsat-core} command.
    \item \bkey{(get-model)}\\
      In the \emph{\mvaltrack}, the \akey{check-sat} command (which is
      always issued in a satisfiable context) is followed by a single
    \akey{get-model} command.
  \item \bkey{(exit)}\\
    It may \emph{optionally} contain an \akey{exit} command as its
    last command.  In the \emph{\inctrack}, this command must not be
    omitted.
  \item \textbf{No other commands} besides the ones just mentioned may be used.
\end{itemize}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

>>>>

Benchmark files are in the concrete syntax of the SMT-LIB format
version~2.6, though with a \emph{restricted} set of commands.  A benchmark
file is a text file containing a sequence of SMT-LIB commands that
satisfies the following \emph{requirements}:
%
\begin{itemize}
  \item
    \bkey{(set-option ...)}
    The input contains the following \akey{set-option} commands.
    \begin{enumerate}[label=(\alph*)]
    \item In the \emph{\inctrack}, the \akey{:print-success} option
      must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
    \item In all other tracks, the scrambler will add an initial
      \akey{(set-option :print-success false)} command to the solver.
    \item In the \emph{\mvaltrack}, a benchmark file contains a single
      \akey{(set-option :produce-models true)} command as the second command.
    \item In the \emph{\ucoretrack}, a benchmark file contains a
      single \akey{(set-option :produce-unsat-cores true)} command as
      the second command.
    \item In the \emph{\prooftrack}, a benchmark file contains a
      single \akey{(set-option :produce-proofs true)} command as
      the second command.
    \end{enumerate}
  \item \bkey{(set-logic ...)}\\
    A (single) \akey{set-logic} command is the \emph{first} command after
    any \akey{set-option} commands.
  \item \bkey{(set-info ...)}\\
    A benchmark file may contain any number of \akey{set-info} commands.
    During the competition all \akey{set-info} commands are removed from
    the benchmark by the scrambler.
  \item \bkey{(declare-sort ...)}\\
    A benchmark file may contain any number of \akey{declare-sort} and
    \akey{define-sort} commands.  All sorts declared or defined with these
    commands must have zero arity.
  \item \bkey{(declare-fun ...)} and \bkey{(define-fun ...)}\\
    A benchmark file may contain any number of \akey{declare-fun} and
    \akey{define-fun} commands.
  \item \bkey{(declare-datatype ...)} and \bkey{(declare-datatypes ...)}\\
    If the logic features algebraic datatypes, the benchmark file may
    contain any number of \akey{declare-datatype(s)} commands.
  \item \bkey{(assert ...)}\\
    A benchmark file may contain any number of \akey{assert} commands.  All
    formulas in the file belong in the declared logic, with any free symbols
    declared in the file.
  \item
    \bkey{:named}
    \begin{enumerate}[label=(\alph*)]
      \vspace{-1ex}
      \item In \emph{all} tracks \emph{except} the \ucoretrack,  named
        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
        used.
      \item In the \emph{\ucoretrack}, top-level assertions may be named.
    \end{enumerate}
  \item
    \bkey{(check-sat)}
    \begin{enumerate}[label=(\alph*)]
      \vspace{-1ex}
    \item In \emph{all} tracks \emph{except} the \inctrack, there is
      \emph{exactly one} \akey{check-sat} command.
    \item In the \emph{\inctrack}, there are one or more
      \akey{check-sat} commands.  There may also be zero or more
      \akey{(push 1)} commands, and zero or more \akey{(pop 1)} commands,
      consistent with the use of those commands in the SMT-LIB standard.
    \end{enumerate}
  \item \bkey{(get-unsat-core)}\\
    In the \emph{\ucoretrack}, the \akey{check-sat} command (which is
    always issued in an unsatisfiable context) is followed by a single
    \akey{get-unsat-core} command.
  \item \bkey{(get-model)}\\
    In the \emph{\mvaltrack}, the \akey{check-sat} command (which is
    always issued in a satisfiable context) is followed by a single
    \akey{get-model} command.
  \item \bkey{(get-proof)}\\
    In the \emph{\prooftrack}, the \akey{check-sat} command (which is
    always issued in an unsatisfiable context) is followed by a single
    \akey{get-proof} command.
  \item \bkey{(exit)}\\
    It may \emph{optionally} contain an \akey{exit} command as its
    last command.  In the \emph{\inctrack}, this command must not be
    omitted.
  \item \textbf{No other commands} besides the ones just mentioned may be used.
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.
